Davos: a Python package ``smuggler'' for constructing lightweight reproducible notebooks

### 2023-07-13 paper/main.tex
edits to metadata table

\begin{abstract}
  Reproducibility is a core requirement of modern scientific research.
  For computational research, reproducibility means that code should
  produce the same results, even when run on different systems.  A
  standard approach to ensuring reproducibility entails packaging a
  project's dependencies along with its primary code base.  Existing
  solutions vary in how deeply these dependencies are specified,
  ranging from virtual environments, to containers, to virtual
  machines.  Each of these existing solutions requires installing or
  setting up a system for running the desired code, increasing the
  complexity and time cost of sharing or engaging with reproducible
  science. Here, we propose a lighter-weight solution: the
  Davos package.  When used in combination with a
  notebook-based Python project, Davos provides a mechanism
  for specifying the correct versions of the project's 
  dependencies directly within the code that requires them, 
  and automatically installing them in an isolated environment 
  when the code is run. The Davos package further
  ensures that those packages and specific versions are used every
  time the notebook's code is executed.  This enables researchers to
  share a complete reproducible copy of their code within a single
  Jupyter notebook file.
\end{abstract}

@@

\begin{table}[H]
\begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
\hline
\textbf{Nr.} & \textbf{Code metadata description} & \textbf{Metadata value} \\
\hline
C1 & Current code version &  v0.1.1 \\
\hline
C2 & Permanent link to code/repository used for this code version & \url{https://github.com/ContextLab/davos/tree/v0.1.1} \\
\hline
C3 & Code Ocean compute capsule & \\
\hline
C4 & Legal Code License & MIT \\
\hline
C5 & Code versioning system used & git \\
\hline
C6 & Software code languages, tools, and services used & Python, JavaScript, PyPI/pip, IPython, Jupyter, ipykernel, PyZMQ. Additional tools used for tests: pytest, Selenium, Requests, Mypy, GitHub Actions \\
\hline
C7 & Compilation requirements, operating environments, and
     dependencies & Dependencies:~Python $\geq 3.6$, packaging, setuptools.~Supported OSes: MacOS, Linux, Unix-like.~Supported IPython environments: Jupyter Notebooks, JupyterLab, Google Colaboratory, Binder, IDE-based notebook editors. \\
\hline
C8 & Link to developer documentation/manual & \url{https://github.com/ContextLab/davos\#readme} \\
\hline
C9 & Support email for questions & contextualdynamics@gmail.com \\
\hline
\end{tabular}
\caption{Code metadata}
\label{}
\end{table}

>>>>

\begin{abstract}
  Reproducibility is a core requirement of modern scientific research.
  For computational research, reproducibility means that code should
  produce the same results, even when run on different systems.  A
  standard approach to ensuring reproducibility entails packaging a
  project's dependencies along with its primary code base.  Existing
  solutions vary in how deeply these dependencies are specified,
  ranging from virtual environments, to containers, to virtual
  machines.  Each of these existing solutions requires installing or
  setting up a system for running the desired code, increasing the
  complexity and time cost of sharing or engaging with reproducible
  science. Here, we propose a lighter-weight solution: the
  Davos package.  When used in combination with a
  notebook-based Python project, Davos provides a mechanism
  for specifying the correct versions of the project's
  dependencies directly within the code that requires them,
  and automatically installing them in an isolated environment
  when the code is run. The Davos package further
  ensures that these packages and specific versions are used every
  time the notebook's code is executed.  This enables researchers to
  share a complete reproducible copy of their code within a single
  Jupyter notebook file.
\end{abstract}

@@

\begin{table}[H]
\begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
\hline
\textbf{Nr.} & \textbf{Code metadata description} & \textbf{Metadata value} \\
\hline
C1 & Current code version &  v0.2.0 \\
\hline
C2 & Permanent link to code/repository used for this code version & \url{https://github.com/ContextLab/davos/tree/v0.2.0} \\
\hline
C3 & Code Ocean compute capsule & \\
\hline
C4 & Legal Code License & MIT \\
\hline
C5 & Code versioning system used & git \\
\hline
C6 & Software code languages, tools, and services used & Python, JavaScript, PyPI/pip, IPython, Jupyter, ipykernel, PyZMQ.\newline Additional tools used for tests: pytest, Selenium, Requests, mypy, GitHub Actions \\
\hline
C7 & Compilation requirements, operating environments, and
     dependencies & Dependencies:~Python $\geq 3.6$, packaging, setuptools.\newline Supported OSes: MacOS, Linux, Unix-like.\newline Supported IPython environments: Jupyter Notebooks, JupyterLab, Google Colaboratory, Binder, IDE-based notebook editors. \\
\hline
C8 & Link to developer documentation/manual & \url{https://github.com/ContextLab/davos\#readme} \\
\hline
C9 & Support email for questions & \href{mailto:contextualdynamics@gmail.com}{contextualdynamics@gmail.com} \\
\hline
\end{tabular}
\caption{Code metadata}
\label{}
\end{table}
